### 2014-05-27 tex/main-body-text.tex
Fixed some $'s so it typeset and changed README to say "use latexmk"
also fixed a pritchardetal

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations. The user must first specify the number of runs (different initial allocation of individuals 
to each cluster) as well as the number of iterations individual has the chance to be reallocated 
to a different cluster. For each run the log-likelihood value of membership to all $K$ clusters is computed
and the difference between the cluster with the highest likelihood and second highest likelihood is reported (LLOD)
for each individual. Runs that converge on the same solution are indicated by the same mean LLOD score. and 
are referred to as a plateau. If for a given $k$ there may be multiple local maxima in addition to 
the global maximum, depending on the initial allocation of individuals the alorithm will result in finding
different plateaus. The plateau record is a list of how many runs ended up at these different solutions. 
\citet{Duc&Tur2012} developed two stopping rules that lead to the estimation of $K$. In the abscence of 
reasonable values for $k$ \citet{Duc&Tur2012} advocate running  {\sc flock} until either a single plateau 
$\geq$6 is reached or four consecutive $k$ values yield no plateaus. If the first stopping condition is satisfied,
the $K$ for which there is a a single plateau $\geq$6 is the point estimate for $K$. Alternatively, 
if multiple plateaus are observed with at least one plateau$\geq$6, the largest value of $K$ that satisfies 
this conditon should be taken as the lower bound estimate of $K$. If no plateaus \geq$6 are observed $K$
is \textit{undecided}.

@@

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in  {\sc structure} \citep{Evannoetal2005, 
Prichardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, no such care in interpreting results 
is suggested in running {\sc flock}. The authors developed estimation rules based on simulated data 
sets with different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}. This may not be as big an issue with small datasets,
however, as sample sizes increase this could have a drastic influence on the estimation of 
K.

>>>>

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations. The user must first specify the number of runs (different initial allocation of individuals 
to each cluster) as well as the number of iterations individual has the chance to be reallocated 
to a different cluster. For each run the log-likelihood value of membership to all $K$ clusters is computed
and the difference between the cluster with the highest likelihood and second highest likelihood is reported (LLOD)
for each individual. Runs that converge on the same solution are indicated by the same mean LLOD score. and 
are referred to as a plateau. If for a given $k$ there may be multiple local maxima in addition to 
the global maximum, depending on the initial allocation of individuals the alorithm will result in finding
different plateaus. The plateau record is a list of how many runs ended up at these different solutions. 
\citet{Duc&Tur2012} developed two stopping rules that lead to the estimation of $K$. In the abscence of 
reasonable values for $k$ \citet{Duc&Tur2012} advocate running  {\sc flock} until either a single plateau 
$\geq 6$  is reached or four consecutive $k$ values yield no plateaus. If the first stopping condition is satisfied,
the $K$ for which there is a a single plateau $\geq 6$ is the point estimate for $K$. Alternatively, 
if multiple plateaus are observed with at least one plateau $\geq 6$, the largest value of $K$ that satisfies 
this conditon should be taken as the lower bound estimate of $K$. If no plateaus $\geq 6$ are observed $K$
is \textit{undecided}.

@@

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in  {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, no such care in interpreting results 
is suggested in running {\sc flock}. The authors developed estimation rules based on simulated data 
sets with different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}. This may not be as big an issue with small datasets,
however, as sample sizes increase this could have a drastic influence on the estimation of 
K.
